\LARGE \bf Matrix Multiplication-Driven Repulsive Fields for 3D Voxel-Based TSDF Calculation

### 2024-03-13 Articles/IROS/root.tex
inverse kinematics control - attractive vel draft

@@

\add{Visualization of the repulsive field around more or less complicated obstacles.}

\begin{figure}[h]
	\centering
	\includegraphics[width=0.95\linewidth]{demo-field1.eps} % Replace 'example-image' with the filename of your image
	\caption{Example Image}
	\label{fig:example-field}
\end{figure}

\add{add label, caption, every plot has different axis scale}

\comment{}{we dont have the close obstacles bottlenecks, we do have weird bottlenecks in the orthagonal directions - maybe}

\subsection{Repulsive Field Interpolation}

\begin{figure}[h]
	\centering
	\includegraphics[width=1\linewidth]{non_and_interp_4_plots.eps} % Replace 'example-image' with the filename of your image
	\caption{Example Image}
	\label{fig:interp-experiment}
\end{figure}

\subsection{Manipulator Examples}

\add{EXAMPLE: MANIPULATOR AND COLUMN}

\add{EXAMPLE: MANIPULATOR AND MOVING NOISY BALL}

\remove{Drone Example}

>>>>

\section{MANIPULATOR KINEMATICS}

\subsection{INVERSE KINEMATIC CONTROL}

The desired movement of the end-effector is achieved by using inverse kinematics velocity control scheme with task prioritisation.

\add{inverse kinematics equation with task prioritization}

\subsection{END-EFFECTOR VELOCITY}

Vodenje vrha manipulatorja (end-effector) je naloga z najvišjo prioriteto.

\remove{Our method employs inverse kinematics approach (IK) to guide the end effector (EE) towards its target, marking a departure from Khatib's joint coordinates approach in favor of a Cartesian coordinates framework. This is particularly beneficial in scenarios involving redundant manipulators, where determining an optimal goal joint configuration in advance is challenging.}

When calculating translational velocity, we avoid the conventional gradient of the squared distance approach, which leads to high initial velocities and subsequently slow speeds near the target. Our aim is a consistent velocity throughout the trajectory, with controlled deceleration near the goal. This is achieved by first calculating the unit vector towards the target for direction, then modulating its magnitude using a sigmoid function, specifically the arctangent function, to prevent overshooting and ensure stable approaching motion.

\begin{equation} 
	\vec{v} = \frac{\vec{x}_{EE} - \vec{x}_g}{||\vec{x}_{EE} - \vec{x}_g||} \times \frac{\arctan(k_{sigm} \; ||\vec{x}_{EE} - \vec{x}_g||) }{pi/2}
	\label{eq: v_att}
\end{equation}

In the above equation (eq.~\ref{eq: v_att}), $\vec{v}$  represents the end effector's translational velocity towards the target, combining direction and magnitude. The terms $\vec{x}_{EE}$ and $\vec{x}_g$ denote the current and goal positions of the EE, respectively, in Cartesian coordinates. The unit vector calculation, $\frac{\vec{x}_{EE}-\vec{x}_g}{||\vec{x}_{EE}-\vec{x}_g||}$, ensures motion directed towards the target. Finally, the sigmoid function, particularly the arctangent component, modulates this velocity to avoid overshooting, balancing speed and precision. The constant $k_{sigm}$ allows us to set how close to the goal does the robot EE start slowing down.

The rotational velocity error of the EE is needed for ensuring goal orientation of the EE. In our approach, orientations are depicted using rotation matrices. Specifically, \( R \) represents the current EE orientation, while \( gR \) signifies the goal EE orientation. The disparity between these orientations is encapsulated by the relative rotation matrix \( dR \). This matrix is formulated by multiplying the goal orientation matrix \( gR \) with the transpose of the current orientation matrix \( cR^{T} \). To ensure that it represents a pure rotation without any scaling we than normalize the so gotten matrix .

\begin{equation}
	dR = \frac{gR \cdot cR^{T}}{||gR \cdot cR^{T}||}
	\label{eq: rot_diff_mat}
\end{equation}

The relative rotation matrix value is converted into a quaternion, which is then logarithmically transformed \remove{to represent the rotational error vectorially}. The components of this quaternion, excluding the real part, than form the rotational error vector \( \omega \).

\begin{equation}
	dR \mapsto dQ = a + b \, i + c \, j + d \, k
	\label{eq: quat_mapsto}
\end{equation}

\begin{equation}
	dQl = 2 \cdot \log(dQ) = al + bl \, i + cl \, j + dl \, k
	\label{eq:quat_log}
\end{equation}

\alert{There needs to be an explanation why log, where is this from. Maybe a reference. cite: DMP Quaternions article Petrič, Žlajpah, Ude}

\begin{equation}
	\vec{\omega} =
	\begin{bmatrix}
		bl \\
		cl \\
		dl
	\end{bmatrix}
	\label{eq:rot_error_vector}
\end{equation}

To get the full velocity of the end effector (EE), \( \mathrm{\vec{v}_{ATT}} \), we combines translational and rotational velocities, which we scale using proportional gains \( k_p \) and \( k_r \).

\begin{equation}
	\mathrm{\vec{v}_{ATT}} = 
	\begin{bmatrix}
		k_p * \vec{v}   \\
		k_{\omega} * \vec{\omega}
	\end{bmatrix}
	\label{eq:ee_velocity}
\end{equation}

Ker uporabljamo preslikavo v ničelni prostor primarne hitrosti (null space), lahko v primeru velikih hitrosti primarne naloge preostane premalo prostostnih stopenj, da bi se lahko varno izognili oviram.

\label{chap:primary slowdown}

To ensure the primary task doesn't overpower the secondary task, we've integrated a primary task execution slowdown. This mechanism can reduce the manipulator's velocity towards its primary goal, leaving more maneuverability space for the secondary tasks.

\begin{equation}
	\label{eq:slowdown}
	\xi_{p}=
	\frac{1}{1 + \kappa_{\text{sec}} \delta_{min}}
\end{equation}

\alert{Is this equation correct, ADD a singularity damping factor. Maybe even some variation of a changing damping.}

The slowdown factor (eq.~\ref{eq:slowdown}) is influenced by the constant \( \kappa_{\text{sec}} \) and the robot's minimum distance from an obstacle \( \delta_{\text{min}} \). We calculate the minimal distance in the repulsive velocities phase of the algorithm, as explained in section~\ref{chap:repulsive velocity}. As per the equation, a large \( \delta_{\text{min}} \) minimizes the slowdown effect, allowing uninterrupted primary task execution. Conversely, a small \( \delta_{\text{min}} \) increases the slowdown, by making the $\xi_{p}$ factor smaller, giving the secondary task more time for corrective actions.

\subsection{AVOIDANCE VELOCITIES}

@@

\add{Visualization of the repulsive field around more or less complicated obstacles.}
%
%\begin{figure}
%	\centering
%	\includegraphics[width=0.95\linewidth]{demo-field1c.eps} % Replace 'example-image' with the filename of your image
%	\caption{Example Image}
%	\label{fig:example-field}
%\end{figure}
%
%\add{add label, caption, every plot has different axis scale}
%
%\comment{}{we dont have the close obstacles bottlenecks, we do have weird bottlenecks in the orthagonal directions - maybe}
%
%\subsection{Repulsive Field Interpolation}
%
%\begin{figure}
%	\centering
%	\includegraphics[width=1\linewidth]{non_and_interp_4_plots.eps} % Replace 'example-image' with the filename of your image
%	\caption{Example Image}
%	\label{fig:interp-experiment}
%\end{figure}
%
%\subsection{Manipulator Examples}
%
%\add{EXAMPLE: MANIPULATOR AND COLUMN}
%
%\begin{figure}
%	\centering
%	\includegraphics[width=1\linewidth]{keyframes_3D.eps} % Replace 'example-image' with the filename of your image
%	\caption{Example Image}
%	\label{fig:keyframes-3d-column}
%\end{figure}
%
%\begin{figure}
%	\centering
%	\includegraphics[width=1\linewidth]{keyframes_2D_a.eps} % Replace 'example-image' with the filename of your image
%	\caption{Example Image}
%	\label{fig:keyframes-2d-column}
%\end{figure}
%
%\begin{figure}
%	\centering
%	\includegraphics[width=1\linewidth]{keyframes_2_columns.eps} % Replace 'example-image' with the filename of your image
%	\caption{Example Image}
%	\label{fig:keyframes-2-column}
%\end{figure}
%
%
%\add{EXAMPLE: MANIPULATOR AND MOVING NOISY BALL}
%
%\begin{figure}
%	\centering
%	\includegraphics[width=1\linewidth]{keyframes_3D_ball.eps} % Replace 'example-image' with the filename of your image
%	\caption{Example Image}
%	\label{fig:keyframes-3d-ball}
%\end{figure}
%
%\begin{figure}
%	\centering
%	\includegraphics[width=1\linewidth]{keyframes_2D_ball.eps} % Replace 'example-image' with the filename of your image
%	\caption{Example Image}
%	\label{fig:keyframes-2d-ball}
%\end{figure}
%
%\begin{figure}
%	\centering
%	\includegraphics[width=0.75\linewidth]{keyframes_2_columns_ball.eps} % Replace 'example-image' with the filename of your image
%	\caption{Example Image}
%	\label{fig:keyframes-2-column-ball}
%\end{figure}
%
%\remove{Drone Example}
